---
title: "Passing Summary Try Out"
author: "Jack DePree"
date: "2023-01-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<http://rmarkdown.rstudio.com>.

```{r}
library(readr)
library(tidyverse)
pff_passing_summary_2012 <- read_csv("pff_passing_summary_2012.csv", show_col_types = FALSE)
pff_passing_summary_2013 <- read_csv("pff_passing_summary_2013.csv", show_col_types = FALSE)
pff_passing_summary_2014 <- read_csv("pff_passing_summary_2014.csv", show_col_types = FALSE)
pff_passing_summary_2015 <- read_csv("pff_passing_summary_2015.csv", show_col_types = FALSE)
pff_passing_summary_2016 <- read_csv("pff_passing_summary_2016.csv", show_col_types = FALSE)
pff_passing_summary_2017 <- read_csv("pff_passing_summary_2017.csv", show_col_types = FALSE)
pff_passing_summary_2018 <- read_csv("pff_passing_summary_2018.csv", show_col_types = FALSE)
pff_passing_summary_2019 <- read_csv("pff_passing_summary_2019.csv", show_col_types = FALSE)
pff_passing_summary_2020 <- read_csv("pff_passing_summary_2020.csv", show_col_types = FALSE)
pff_passing_summary_2021 <- read_csv("pff_passing_summary_2021.csv", show_col_types = FALSE)
pff_passing_summary_2022 <- read_csv("pff_passing_summary_2022.csv", show_col_types = FALSE)
```

```{r}
  # Assigning the tables to smaller names
pass_12 <- pff_passing_summary_2012
pass_13 <- pff_passing_summary_2013
pass_14 <- pff_passing_summary_2014
pass_15 <- pff_passing_summary_2015
pass_16 <- pff_passing_summary_2016
pass_17 <- pff_passing_summary_2017
pass_18 <- pff_passing_summary_2018
pass_19 <- pff_passing_summary_2019
pass_20 <- pff_passing_summary_2020
pass_21 <- pff_passing_summary_2021
pass_22 <- pff_passing_summary_2022
  # Merging the 'prior' season to the 'current' season
pass_12_13 <- merge(pass_12, pass_13, by='player', all=TRUE, suffixes=c('.x','.y'))
pass_13_14 <- merge(pass_13, pass_14, by='player', all=TRUE, suffixes=c('.x','.y'))
pass_14_15 <- merge(pass_14, pass_15, by='player', all=TRUE, suffixes=c('.x','.y'))
pass_15_16 <- merge(pass_15, pass_16, by='player', all=TRUE, suffixes=c('.x','.y'))
pass_16_17 <- merge(pass_16, pass_17, by='player', all=TRUE, suffixes=c('.x','.y'))
pass_17_18 <- merge(pass_17, pass_18, by='player', all=TRUE, suffixes=c('.x','.y'))
pass_18_19 <- merge(pass_18, pass_19, by='player', all=TRUE, suffixes=c('.x','.y'))
pass_19_20 <- merge(pass_19, pass_20, by='player', all=TRUE, suffixes=c('.x','.y'))
pass_20_21 <- merge(pass_20, pass_21, by='player', all=TRUE, suffixes=c('.x','.y'))
pass_21_22 <- merge(pass_21, pass_22, by='player', all=TRUE, suffixes=c('.x','.y'))
  # Joining all of the merged tables into on table for ease of analysis
passing_12_22 <- rbind(pass_12_13, pass_13_14, pass_14_15, pass_15_16, pass_16_17, pass_17_18, pass_19_20, pass_20_21, pass_21_22)
passing_12_22
  # Showing the index for each column
column.passing <- names(passing_12_22)
numbers <- 1:83
index.passing <- data.frame(numbers, column.passing)
index.passing
```

\*\*Analysis

Plotting

```{r}
yards.cor <- c()
tds.cor <- c()
yards.y <- passing_12_22$yards.y
tds.y <- passing_12_22$touchdowns.y

for (i in seq(5,42,1)) {
  jj <- cor(yards.y, passing_12_22[i], use="complete.obs")
  yards.cor <- c(yards.cor, jj)
}
for (i in seq(5,42,1)) {
  jj <- cor(tds.y, passing_12_22[i], use="complete.obs")
  tds.cor <- c(tds.cor, jj)
}

plot(yards.cor, xlab="Index", ylab="Yards Correlation", col="blue", cex=2, lwd=2)
points(tds.cor, col="red", cex=2, lwd=2)

yards.cor.60 <- colnames(passing_12_22[which(yards.cor>=.6)+4])
yards.cor.60
```

Conditional Probabilities Test

Hypothetical Methodology 1: Make lists of probabilities for each condition (a list of probabilities for "game_count" and for the future year's variable at a percentile of 90, and then another list for the same variable at a percentile of 80). Then, make a list of lists for each variable and their various conditions and outcomes. Then, make a list of lists for all of the variables of the columns.

Hypothetical Methodology 2: Make lists of probabilities for each "repetitional" condition (each "repetitional" outcome is the odds that a player will repeat the next year at the same level, meaning if a player passes 90th yards.x then what are the odds they get 90th yards.y?).


Average If data.frame Test

```{r}
zscores <- c(2.5, 2, 1.5, 1, .5, 0, -.5, -1, -1.5, -2, -2.5)
zpercentiles <- c(.9938, .9772, .9332, .8413, .6915, .5, .3085, .1587, .0668, .0228, .0062)

z.score <- data.frame(zscores, zpercentiles)
z.score
```

Implementation

i need a loop that makes a list of all of the implied yards per each variable for each player, then to take the average of that list, then make a new list of the players + their mean(implied.yards) + their actual yards

Make a list of the filtered columns of passing_12_22. The make a loop that goes through the list of columns, then makes a new list of the associated average.if.predictions


Polynomial Regression

```{r}
passing_12_22.sub <- na.omit(passing_12_22)
game.count.na <- passing_12_22.sub$player_game_count.x
yards.y.na <- passing_12_22.sub$yards.y

model.game.count <- lm(yards.y.na ~ poly(game.count.na, 3, raw=TRUE))

#summary(model.game.count)
coef(model.game.count)

#confint(model.game.count, level=.96)

#plot(fitted(model.game.count), residuals(model.game.count))

yards.n.cor <- c()
for (i in seq(5,42,1)) {
  jj <- cov(yards.y.na, passing_12_22.sub[i])
  yards.n.cor <- c(yards.n.cor, jj)
}
yards.n.cor
yards.n.cor.50th <- colnames(passing_12_22.sub[which(yards.n.cor>=5600)+4])
yards.n.cor.50th

ggplot(passing_12_22.sub, aes(player_game_count.x, yards.y)) +
  geom_point() + stat_smooth(method=lm, formula=y~poly(x,3,raw=TRUE))

```

Testing / Examples

```{r}
df.data <- data.frame(x1 = 1:5)                            # Old data
      

for(i in 1:5) {                                            # Head of for-loop
  new.col <- (5)                             # Create and fill new column
  df.data[, ncol(df.data) + 1] <- new.col                  # Append new column
  colnames(df.data)[ncol(df.data)] <- paste0("new", i)     # Rename column name
}
for (i in 1:3) {
  new.row <- (3)                             # Create and fill new row
  df.data[nrow(df.data) + 1, ] <- new.row                   # Append new row
  }
df.data
```
  

```{r}
pass.variables <- colnames(passing_12_22[5:42])
average.if <- data.frame(Tier="10th")
yards.y <- passing_12_22$yards.y
means <- data.frame(variable=numeric())

for (i in 1:38) {
  for (xx in 1:10) {
    variable <- passing_12_22[,i+4]
    bottom <- quantile(variable, zpercentiles[xx+1], na.rm=TRUE)
    top <- quantile(variable, zpercentiles[xx], na.rm=TRUE)
    mean <- mean(yards.y[variable >= bottom & variable <= top], na.rm=TRUE)
    means[nrow(means) + 1,] <- mean
    
  }
  new.col <- (means)
  average.if[, ncol(average.if) + 1] <- new.col
  colnames(average.if)[ncol(average.if)] <- paste0(pass.variables[i])
}
average.if


```

```{r}
means <- data.frame(variable=numeric())
for (xx in 1:10) {
    variable <- passing_12_22[1+4]
    bottom <- quantile(variable, zpercentiles[xx+1], na.rm=TRUE)
    top <- quantile(variable, zpercentiles[xx], na.rm=TRUE)
    mean <- mean(yards.y[variable >= bottom & variable <= top], na.rm=TRUE)
    means[nrow(means) + 1,] <- mean
}
means
```


```{r}
pass.variables <- colnames(passing_12_22[5:42])
average.if <- data.frame(Tier="10th")
yards.y <- passing_12_22$yards.y
for (i in 1:38) {
  variable <- passing_12_22[,i+4]
  bottom <- quantile(variable, zpercentiles[11], na.rm=TRUE)
  top <- quantile(variable, zpercentiles[10], na.rm=TRUE)
  means <- mean(yards.y[variable >= bottom & variable <= top], na.rm=TRUE)
  
  new.col <- (means)
  average.if[, ncol(average.if) + 1] <- new.col
  colnames(average.if)[ncol(average.if)] <- paste0(pass.variables[i])
}
average.if

```








