---
title: "Within_Season_QB"
author: "Jack DePree"
date: "2024-03-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Within Season Projections for Quarterbacks

## Contextualization
A within season projection for quarterbacks is a statistical model that predicts the performance of a quarterback in the upcoming weeks of the season. This model is useful for fantasy football players who are looking to make informed decisions about which players to start in their lineups and how to value players throughout an ongoing season. By using historical data on quarterback performance, there are insights about predictability, attribute importance, model evaluation and individual value.

## Reasoning
With more and more data from previous weeks (weekly sample size), there should be more and more accurate predictions and validity of decisions with individual quarterbacks. There should be predictive value in specific attributes relative to the current standing within the season creating quantifiable projections for individuals quarterbacks. 

## Scientific Questions
1. Which attributes in the data set are most important for predicting the rest of the data for each weekly sample size? (PCA)
2. Which attributes are most highly associated with the year-end fantasy points, and how do they change per sample size? (Feature Selection)
3. How do visualizations explain the relationship between attributes and the year-end fantasy points? (Data Visualization)
4. Is there a model that can predict the year-end fantasy points for quarterbacks? (Regression Analysis)
5. Is there a machine learning model that can predict the year-end fantasy points for quarterbacks? (SVM)

## Methodology
1. Transform data into multiple data frames for each weekly sample size (2019 - 2023). Perform a PCA to determine the most important attributes for each weekly sample size, and compare the results.
2. Perform a correlation test to determine the most important attributes for predicting the year-end fantasy points for each weekly sample size, and compare the results.
3. Create visualizations to explain the relationship between attributes and the year-end fantasy points for each weekly sample size.
4. Perform a regression analysis to determine if there is a model that can predict the year-end fantasy points for quarterbacks for each weekly sample size. Use historical data as the training set; use the 2023 season as the testing set.
5. Perform a SVM analysis to determine if there is a machine learning model that can predict the year-end fantasy points for quarterbacks for each weekly sample size. Use historical data as the training set; use the 2023 season as the testing set.

```{r}

directory <- getwd() #get the current working directory
code_loc <- "/code" #make string to remove from current working directory
directory <- gsub(code_loc, "", directory) #remove string from current working directory
data_loc <- "/data" #make string to add to the current working directory
new_directory <- paste0(directory, data_loc) #add the data string to the working directory
setwd(new_directory) #set the working directory

library(dplyr)
library(tidyverse)

wk1_23 <- read.csv("2023_wk1_qb_stats.csv")
wk2_23 <- read.csv("2023_wk2_qb_stats.csv")
wk3_23 <- read.csv("2023_wk3_qb_stats.csv")
total_23 <- read.csv("2023_total_qb_stats.csv")

wk1_22 <- read.csv("2022_wk1_qb_stats.csv")
wk2_22 <- read.csv("2022_wk2_qb_stats.csv")
wk3_22 <- read.csv("2022_wk3_qb_stats.csv")
wk4_22 <- read.csv("2022_wk4_qb_stats.csv")
wk5_22 <- read.csv("2022_wk5_qb_stats.csv")
wk6_22 <- read.csv("2022_wk6_qb_stats.csv")
wk7_22 <- read.csv("2022_wk7_qb_stats.csv")
wk8_22 <- read.csv("2022_wk8_qb_stats.csv")
wk9_22 <- read.csv("2022_wk9_qb_stats.csv")
wk10_22 <- read.csv("2022_wk10_qb_stats.csv")
wk11_22 <- read.csv("2022_wk11_qb_stats.csv")
wk12_22 <- read.csv("2022_wk12_qb_stats.csv")
wk13_22 <- read.csv("2022_wk13_qb_stats.csv")
wk14_22 <- read.csv("2022_wk14_qb_stats.csv")
wk15_22 <- read.csv("2022_wk15_qb_stats.csv")
wk16_22 <- read.csv("2022_wk16_qb_stats.csv")
wk17_22 <- read.csv("2022_wk17_qb_stats.csv")
total_22 <- read.csv("2022_total_qb_stats.csv")

wk1_21 <- read.csv("2021_wk1_qb_stats.csv")
wk2_21 <- read.csv("2021_wk2_qb_stats.csv")
wk3_21 <- read.csv("2021_wk3_qb_stats.csv")
wk4_21 <- read.csv("2021_wk4_qb_stats.csv")
wk5_21 <- read.csv("2021_wk5_qb_stats.csv")
wk6_21 <- read.csv("2021_wk6_qb_stats.csv")
wk7_21 <- read.csv("2021_wk7_qb_stats.csv")
wk8_21 <- read.csv("2021_wk8_qb_stats.csv")
wk9_21 <- read.csv("2021_wk9_qb_stats.csv")
wk10_21 <- read.csv("2021_wk10_qb_stats.csv")
wk11_21 <- read.csv("2021_wk11_qb_stats.csv")
wk12_21 <- read.csv("2021_wk12_qb_stats.csv")
wk13_21 <- read.csv("2021_wk13_qb_stats.csv")
wk14_21 <- read.csv("2021_wk14_qb_stats.csv")
wk15_21 <- read.csv("2021_wk15_qb_stats.csv")
wk16_21 <- read.csv("2021_wk16_qb_stats.csv")
wk17_21 <- read.csv("2021_wk17_qb_stats.csv")
total_21 <- read.csv("2021_total_qb_stats.csv")

wk1_20 <- read.csv("2020_wk1_qb_stats.csv")
wk2_20 <- read.csv("2020_wk2_qb_stats.csv")
wk3_20 <- read.csv("2020_wk3_qb_stats.csv")
wk4_20 <- read.csv("2020_wk4_qb_stats.csv")
wk5_20 <- read.csv("2020_wk5_qb_stats.csv")
wk6_20 <- read.csv("2020_wk6_qb_stats.csv")
wk7_20 <- read.csv("2020_wk7_qb_stats.csv")
wk8_20 <- read.csv("2020_wk8_qb_stats.csv")
wk9_20 <- read.csv("2020_wk9_qb_stats.csv")
wk10_20 <- read.csv("2020_wk10_qb_stats.csv")
wk11_20 <- read.csv("2020_wk11_qb_stats.csv")
wk12_20 <- read.csv("2020_wk12_qb_stats.csv")
wk13_20 <- read.csv("2020_wk13_qb_stats.csv")
wk14_20 <- read.csv("2020_wk14_qb_stats.csv")
wk15_20 <- read.csv("2020_wk15_qb_stats.csv")
wk16_20 <- read.csv("2020_wk16_qb_stats.csv")
wk17_20 <- read.csv("2020_wk17_qb_stats.csv")
total_20 <- read.csv("2020_total_qb_stats.csv")

wk1_19 <- read.csv("2019_wk1_qb_stats.csv")
wk2_19 <- read.csv("2019_wk2_qb_stats.csv")
wk3_19 <- read.csv("2019_wk3_qb_stats.csv")
wk4_19 <- read.csv("2019_wk4_qb_stats.csv")
wk5_19 <- read.csv("2019_wk5_qb_stats.csv")
wk6_19 <- read.csv("2019_wk6_qb_stats.csv")
wk7_19 <- read.csv("2019_wk7_qb_stats.csv")
wk8_19 <- read.csv("2019_wk8_qb_stats.csv")
wk9_19 <- read.csv("2019_wk9_qb_stats.csv")
wk10_19 <- read.csv("2019_wk10_qb_stats.csv")
wk11_19 <- read.csv("2019_wk11_qb_stats.csv")
wk12_19 <- read.csv("2019_wk12_qb_stats.csv")
wk13_19 <- read.csv("2019_wk13_qb_stats.csv")
wk14_19 <- read.csv("2019_wk14_qb_stats.csv")
wk15_19 <- read.csv("2019_wk15_qb_stats.csv")
wk16_19 <- read.csv("2019_wk16_qb_stats.csv")
wk17_19 <- read.csv("2019_wk17_qb_stats.csv")
total_19 <- read.csv("2019_total_qb_stats.csv")
```

```{r}




```

***

# Data Cleaning

***

```{r}
#separate()
#mutate()
#transmute()
#select()
#relocate()
#na.omit()

```

```{r}

```

***

# Data Transformation

***

```{r}
#merge()
#rbind()

```

```{r}

```

***

# Data Analysis

***

```{r}
#summary()
#cor()
#quantile()
#group_by()
#sapply()
#lm()

```

```{r}
modeller <- function(dat, indep, dep) {
  indep <- colnames(dat[, indep])
  dep <- grep(dep, colnames(dat))
  data <- dat %>% select(c(all_of(indep), dep)) %>% na.omit()
  intercept_only <- lm(dat[,dep] ~ 1, data=data)
  all <- lm(dat[,dep] ~ ., data=data)
  model <- step(intercept_only, direction="forward", scope=formula(all), trace=0)
  summary(model)
}
```

***

# Data Visualization

***

```{r}
#ggplot()
#geom_smooth()

```

```{r}

```

***

# Regression Analysis

***

```{r}

```

```{r}

```